---
title: "Task3"
author: "Kirill Tumanov"
date: "16 10 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Package
```{r}
library(tidyverse)
```

#Transforming data
```{r warning=FALSE}
data17 <-  read_fwf("Nat2017PublicUS.c20180516.r20180808.txt", fwf_positions (start = c(475, 504, 13), end = c(475, 507, 14), col_names = c("sex","weight","month")))
data18 <- read_fwf("Nat2018PublicUS.c20190509.r20190717.txt", fwf_positions (start = c(475, 504, 13), end = c(475, 507, 14), col_names = c("sex","weight","month")))
```
 
#Adding columns
```{r}
data17$year <- 2017
data18$year <- 2018
```

#Merging tables
```{r warning=FALSE}
datalist <- full_join (data17,data18)
```

#Cleaning
```{r}
datalist$weight <- as.numeric(datalist$weight)
datalist$month <- as.numeric(datalist$month)
datalist$weight[datalist$weight == 9999] <- NA
```

#Question 1
What is the proportion of boys to girls? Has it changed between 2017 and 2018?
```{r}
prop17 <- nrow(datalist[datalist$sex == "M" & datalist$year == 2017,]) / nrow(datalist[datalist$sex == "F" & datalist$year == 2017,])
prop18 <- nrow(datalist[datalist$sex == "M" & datalist$year == 2018,]) / nrow(datalist[datalist$sex == "F" & datalist$year == 2018,])
```
The proportion of boys to girls is almost equal. In both years boys were born a little more than girls.
In 2017 the proportion cosists 1.048 and in 2018 the proportion composes 1.046. The proportion has changed a little bit.
More girls were born in 2018 to compare to 2017.

#Question 2
What is the average birth weight in grams?
```{r}
averweight <- mean(datalist$weight, na.rm = TRUE)
```
The average birth weight for a child is 3261.89 in grams.

#Plot
A density plot on the birth weight between boys and girls in 2018
```{r}
datalist[datalist$year == 2018,] %>%
  ggplot(aes(x = weight, group = sex, col = sex)) +
  geom_density() +
  labs(x = "Weight", y = "Density", title = "The birth weight between boys and girls in 2018")
```

#Question 3
Does the average birth weight vary by month and year?
```{r}
aver <- datalist %>%
  group_by(month,year) %>%
  summarise(averageweight = mean(weight,na.rm = TRUE))
```
It is clearly seen, that the average birth weight vary by month and year, but the differences are usually only a few grams.

